\section{Limitations}

Although the current prototype is sufficient for a course project and already supports real-mainnet case studies, its scope is still intentionally limited. The implemented detector only covers Aave V3, Balancer V2, and Uniswap V2, and the report focuses on official or canonical deployments rather than every fork, wrapper, or flash-loan-capable system on Ethereum. As a result, the current prototype should be understood as a multi-protocol but not protocol-complete detector.

The current evaluation scope is also limited. The reported real-mainnet run is based on a small validation window and is mainly used to confirm that the extraction, verification, aggregation, and export pipeline can correctly explain real representative samples. This is strong enough for demonstrating real-sample detection capability, but it is not yet sufficient for broad claims about chain-wide coverage, protocol prevalence, asset popularity, or robust precision and recall over a large benchmark.

Finally, the project focuses on recognizing flash-loan-like execution patterns rather than fully reconstructing user intent. The scanner can show that a transaction matches a flash-loan or flash-swap structure and can explain why the interaction is labeled as \texttt{verified} or \texttt{strict}. However, it does not yet automatically classify the downstream strategy in a fine-grained way, such as distinguishing among arbitrage, liquidation, refinancing, or attack behavior. These limitations do not invalidate the prototype, but they define the boundary of the claims that this report can responsibly make.
